### 2018-07-05 paper/6-engineering.tex
Minor fixes

\item[Communication] When traces or contents are stored on a central server
communication can become a bottleneck, so it is important to send only the
minimum amount of information, optimising with respect to build-system specific
invariants.

>>>>

\item[Communication] When traces or contents are stored in the cloud
communication can become a bottleneck, so it is important to send only the
minimum amount of information, optimising with respect to build system
invariants. For example, incremental data processing systems in the cloud, such
as \Reflow~\cite{reflow}, need to efficiently orchestrate terabytes of data.
